---
title: "Results"
author: "Steven R. Corsi, Laura A. De Cicco and others"
date: "November 30, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Results {#results}

```{r,echo=FALSE}
library(dplyr)
dfHM <- readRDS("../../process/out/combined_human_markers.rds")
occur <- function(x) mean(x>225)
dfHM_summary <- dfHM %>% 
  group_by(scale) %>%
  summarize(n = length(bacHum))
dfHM$hm <- dfHM$bacHum + dfHM$lachno2

maxHM <- round(max(dfHM$hm)/10^9,2)
maxSite <- dfHM[which.max(dfHM$hm),"site"]
maxScale <- dfHM[which.max(dfHM$hm),"scale"]
```
Throughout the study, `r sum(dfHM_summary$n)` samples were collected, including `r dfHM_summary[1,"n"]` samples from `r dfHM_summary[1,"scale"]` scale sites, `r dfHM_summary[2,"n"]` samples from `r dfHM_summary[2,"scale"]` scale sites, and `r dfHM_summary[3,"n"]` samples from `r dfHM_summary[3,"scale"]` scale sites. The sum of the two human indicator bacteria markers (hereafter referred to as HIB) varied from below the reporting level to a maximum of `r maxHM` x 10^9^ cn/100 ml (Figure 2).



```{r figure_2, fig.width=5,fig.height=5, fig.cap = "Figure 2. The sum of human indicator bacteria markers A. concentrations and b. Occurrence proportion in samples from small storm sewers and open channels (small scale), subwatersheds of the Milwaukee River (subwatershed scale), and tributaries of the Great Lakes (watershed scale). For each scale, sites are ordered by most to least urban land use percentage from left to right.", echo=FALSE}
#source(file = #file.path("plots","out","Figure_2_bar_box.png"))
#fig_2 <- plot_fig_2()
print(fig_2)

```

``` {r, echo = FALSE}
# Determine several parameters to help describe the results
#1. Differences within the small scale
dfSmall <- dfHM %>% filter(scale=="small")
WI_ratio <- round(mean(dfSmall[which(dfSmall$site=="WI"),"hm"])/mean(dfSmall[which(dfSmall$site!="WI"),"hm"]),0)
WI_ratio_median <- round(median(dfSmall[which(dfSmall$site=="WI"),"hm"])/median(dfSmall[which(dfSmall$site!="WI"),"hm"]),0)
#confirmed p< 0.05
wilcox.result <- wilcox.test(dfSmall[which(dfSmall$site=="WI"),"hm"],dfSmall[which(dfSmall$site!="WI"),"hm"]) 
hmMINYEvent <- dfSmall[which(dfSmall$site!="WI" & dfSmall$hydro_cond=="Event"),"hm"]
hmMINYLowflow <- dfSmall[which(dfSmall$site!="WI" & dfSmall$hydro_cond!="Event"),"hm"]
wilcox.result2 <- wilcox.test(hmMINYEvent,hmMINYLowflow)

#See explor_hb_concentrations for tests of event vs low flow for subwatershed scale and watershed scale
#for sites with > 25% urban vs sites with < 25% urban

```
There were differences in HB concentrations among sites and by hydrologic condition. At the small scale, median concentrations of HB were `r WI_ratio_median` times greater at the Wisconsin sites than those from the other states (p < 0.05). In samples from Michigan and New York, results indicated greater HB concentrations during runoff events than during periods of low flow (p < 0.05), but results from the small scale Wisconsin sites indicated no significant difference in HB concentrations by hydrologic event. 

Samples collected at sites with greater than 25% urban land cover at the watershed and subwatershed scales had greater HB concentrations during runoff event periods than low-flow periods (p<0.05). Concentrations of HIB at sites with less than 25% urban land cover at these two scales were not significantly different. 


Actions needed:
1. Develop site characteristics table. Land cover for the watershed and subwatershed scales, and for the three primary small watersheds in the small scale.
    + need site IDs for middle branch Clinton and Red Creek, NY
2. Use these characteristics to describe the hydrologic changes. Urban: hydro change, non-urban no hydro change.



Points to make with this figure:

1. Small scale
    +Wisconsin small scale had samples with max concentrations and were generally higher than other sites
2. Medium scale
    + difference in event vs low flow for more urban sites.
3. Many sites had greater concentrations during runoff events. This is true for the watersheds and subwatersheds that had substantial urban influence. 
    + Look into urban influence vs ratio of event to low flow?
4. Seasonality? 
    + Reference GLRI report?
 
Do we want a similar descriptive set of graphs for some of the optical properties? maybe for SI?

1. ordered list
2. item 2
    + sub-item 1
    + sub-item 2 