---
title: "Results"
author: "Steven R. Corsi, Laura A. De Cicco and others"
date: "November 30, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Results {#results}

```{r,echo=FALSE}
dfHM <- readRDS("../../process/out/combined_human_markers.rds")
occur <- function(x) mean(x>225)
dfHM_summary <- dfHM %>% 
  group_by(scale) %>%
  summarize(n = length(bacHum))

maxHM <- round(max(dfHM$bacHum + dfHM$lachno2)/10^9,2)
maxSite <- dfHM[which.max(dfHM$bacHum + dfHM$lachno2),"site"]
maxScale <- dfHM[which.max(dfHM$bacHum + dfHM$lachno2),"scale"]
```
Throughout the study, `r sum(dfHM_summary$n)` samples were collected, including `r dfHM_summary[1,"n"]` samples from `r dfHM_summary[1,"scale"]` scale sites, `r dfHM_summary[2,"n"]` samples from `r dfHM_summary[2,"scale"]` scale sites, and `r dfHM_summary[3,"n"]` samples from `r dfHM_summary[3,"scale"]` scale sites. The sum of the two human markers varied from below the reporting level to a maximum of `r maxHM` x 10^9^ cn/100 ml at a `r maxScale` scale site in `r maxSite` during a runoff event period (Figure 2).



```{r figure_2, fig.cap = "Figure 2. Human bacteria marker A. concentrations and b. Occurrence proportion in samples from small storm sewers and open channels (Small), subwatersheds of the Milwakee River (Subwatersheds), and tributaries of the Great Lakes (Watershed)", echo=FALSE}
#source(file = #file.path("plots","out","Figure_2_bar_box.png"))
#fig_2 <- plot_fig_2()
print(fig_2)

```



Points to make with this figure:
1. Wisconsin small scale had samples with max concentrations and were generally higher than other sites
2. Many sites had greater concentrations during runoff events. This is true for the watersheds and subwatersheds that had substantial urban influence. 
3. Small scale sites
