---
title: "Results"
author: "Steven R. Corsi, Laura A. De Cicco, Angela Hanson, Peter Lenaker, Brian Bergamaschi, Brian Pellerin"
date: ""
#output: word_document
output:
  bookdown::word_document2:
#    css: environmental-science-and-technology.csl
    fig_caption: yes
    toc: no
    reference_docx: "word-styles-reference-orig.docx"
#bibliography: Optical properties.bib
#link-citations: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
knitr::opts_knit$set(root.dir = '../../') 
```

```{r some_resources, echo=FALSE}

# Resources: 
# Commonly used symbols in R Markdown: https://people.ok.ubc.ca/jpither/modules/Symbols_markdown.html
```


```{r read_sites, echo=FALSE}


model_summary <- readRDS("model/out/modeling_summary_table.rds")
model_summary$Bachuman <- sub("Turbidity_mean","Turb",model_summary$Bachuman)
model_summary$Bachuman <- sub("Turb","Turbidity",model_summary$Bachuman)
vars <- unique(unlist(strsplit(model_summary$Bachuman,split = "_")))
var_names <- c("Turbidity","F","T","M","N","A290","A295","T2","Turbidity")


font_size <- 4

```

# Methods

## Regression modeling

**Describe the way models were chosen**

  - ~~minimizing the median cross validated sum of squared errors~~
  - ~~examining each model for reasonable description of variability for all sites included. At times there were reasonable regressions overall, but one or more sites did not fit well. These models were not chosen.~~
  + Groupings of sites
    + All sites
    + Elimination of JI (seiche)
    + Groupings of like sites 
    + Urban
    + Ag
    + JI only
        + test
    + Only sites with at least 15 detections
    
Regression modeling was used to explore relations between bacteria concentrations (response variables) and optical signals (explanatory variables). In all cases, response variables were log base 10 transformed. From a practical standpoint for potential field application, explanatory variable selection for these regressions was done in two potential stages: First, optical signals measured in the laboratory that represent signals available in current field sensors were considered (case 1). Next, explanatory variables were expanded to use of additional optical signals and variables that were derived from optical signals. Only those variables that were not correlated to the field sensor signals with a correlation coefficient of 0.95 or greater were considered. These signals included direct fluorescence or absorbance signals at specific wavelengths, means of fluorescence or absorbance signals over specified bandwidths, ratios of these signals, spectral slopes determined as the slope of the absorbance curve over specified wavelengths in exponential space (**<span custom-style="OrangeText">add reference here</span>**), and several optical indices that have been used in previous research (**<span custom-style="OrangeText">add references here</span>**). Given the potential for seasonality in DOC composition in streams (@kaiser_seasonal_2001, @coble_temporal_2016), seasonal varaibles (sine and cosine of julian day/(2$\pi$)) were used to develop interaction terms with optical signals. Optical signals used as case 1 variables included signals F (commonly called fDOM or CDOM) and T (often referred to as tryptophan-like fluorescence) as well as turbidity. Final explanatory variables used in this analysis are presented in the supporting information (Table SI-xx).

The model selection process included several steps with the ultimate goal of minimizing error in prediction while choosing a model that has a reasonable fit for all sites in the data set. It was not uncommon to find a model that appeared to be a good fit overall but did not provide a good fit for data from one or more of the  individual sites. For this reason, exploration of potential regression models was conducted using data sets that included multiple sites as well as one single-site data set (Milwaukee River). The Milwaukee River was modeled independently from other sites because the nature of organic matter influence was substantially different than other sites: The moniotoring station at this site was near Lake Michigan and a seiche effect is commonly present, posing the potential for Lake Michigan water influence. In addition, sites with similar land cover were grouped into one data set (e.g. urban, agrucultural). For the single-site data set, ordinary least squares regression (OLS) was used. For data sets with more than one site included, linear heirarchical mixed effects models (LME) were used to account for potential shifts in the statistical relationships among sites (**<span custom-style="OrangeText">add references for base r and lme4</span>**). For both modeling techniques, 5-fold cross validation repeated 50 times was conducted to estimate predictive accuracy. The median root mean squared residuals (RMSE) for the 50 fits was used to compare among models with different explanatory variable combinations. For models that included only one site (Milwaukee River), the model with the lowest median sum of RMSE was chosen. For models that included multiple sites, model options within 3% of the of the lowest median sum of RMSE were evaluated further by considering the quality of fit for each individual site. The RMSE was computed individual sites, and the maximum and minimum individual site RMSE values for each model were identified. The final model was chosen based on the smallest difference between the maximum and minimum individual site RMSE. This minimized the chances of choosing a multiple-site model with a poor fit for individual sites. 

# Results {#results}

```{r,echo=FALSE}
library(tidyverse)
library(ggplot2)
library(scales)
library(cowplot)
library(flextable)
library(officer)

dfHM <- readRDS("process/out/combined_human_markers.rds")
occur <- function(x) mean(x>225)
dfHM_summary <- dfHM %>% 
  group_by(scale) %>%
  summarize(n = length(bacHum))
dfHM$hm <- dfHM$bacHum + dfHM$lachno2

maxHM <- round(max(dfHM$hm)/10^9,2)
maxSite <- dfHM[which.max(dfHM$hm),"site"]
maxScale <- dfHM[which.max(dfHM$hm),"scale"]

source(file = "plots/src/Figure_2.R")
source(file = "plots/src/Figure_3.R")
source(file = "plots/src/Figure_4.R")

ConcOccurrenceFig <- plot_fig_2()
bacteria_vs_virus <- plot_fig_3()
Prediction_vs_virus <- plot_fig_4()

```
Throughout the study, `r sum(dfHM_summary$n)` samples were collected, including `r dfHM_summary[1,"n"]` samples from `r dfHM_summary[1,"scale"]` scale sites, `r dfHM_summary[2,"n"]` samples from `r dfHM_summary[2,"scale"]` scale sites, and `r dfHM_summary[3,"n"]` samples from `r dfHM_summary[3,"scale"]` scale sites. The sum of the two human indicator bacteria markers (hereafter referred to as sHM) varied from below the reporting level to a maximum of `r maxHM` x 10^9^ cn/100 ml (Figure \@ref(fig:ConcAndOccurrenceFig)).



```{r ConcAndOccurrenceFig, dpi=300, fig.width=3,fig.height=5, fig.cap = "The sum of human indicator bacteria markers A. concentrations and B. Occurrence proportion in samples from small storm sewers and open channels (small scale), subwatersheds of the Milwaukee River (subwatershed scale), and tributaries of the Great Lakes (watershed scale). For each scale, sites are ordered by most to least urban land use percentage from left to right. Number of observations in each concentration bin are provided above the bars.", echo=FALSE}

print(ConcOccurrenceFig)

```

<div custom-style="RedText">Do we want a similar descriptive set of graphs for some of the optical properties? maybe for SI?</div>

<div custom-style="RedText">Add graph with variability of sewage samples? Here or SI?</div>



``` {r, echo = FALSE}
# Determine several parameters to help describe the results
#1. Differences within the small scale
dfSmall <- dfHM %>% filter(scale=="small")
WI_ratio <- round(mean(dfSmall[which(dfSmall$site=="WI"),"hm"])/mean(dfSmall[which(dfSmall$site!="WI"),"hm"]),0)
WI_ratio_median <- round(median(dfSmall[which(dfSmall$site=="WI"),"hm"])/median(dfSmall[which(dfSmall$site!="WI"),"hm"]),0)
#confirmed p< 0.05
wilcox.result <- wilcox.test(dfSmall[which(dfSmall$site=="WI"),"hm"],dfSmall[which(dfSmall$site!="WI"),"hm"]) 
hmMINYEvent <- dfSmall[which(dfSmall$site!="WI" & dfSmall$hydro_cond=="Event"),"hm"]
hmMINYLowflow <- dfSmall[which(dfSmall$site!="WI" & dfSmall$hydro_cond!="Event"),"hm"]
wilcox.result2 <- wilcox.test(hmMINYEvent,hmMINYLowflow)

#See explor_hb_concentrations for tests of event vs low flow for subwatershed scale and watershed scale
#for sites with > 25% urban vs sites with < 25% urban

```


There were differences in sHM concentrations among sites and by hydrologic condition (Figure \@ref(fig:ConcAndOccurrenceFig)). At small-scale sites, median concentrations of sHM were `r WI_ratio_median` times greater in samples from the Wisconsin sites collected in the Kinnickinic River system than those from the other states (p < 0.05). In samples from small-scale sites in Michigan (Middle Branch Clinton River) and New York (Red Creek), results indicated greater sHM concentrations during runoff events than during periods of low flow (p < 0.05), but results from the small scale sites in Wisconsin indicated no significant difference in sHM concentrations by hydrologic condition. 

Samples collected at sites with greater than 25% urban land cover at the watershed and subwatershed scales had greater sHM concentrations during runoff event periods than low-flow periods (p<0.05). Concentrations of sHM at sites with less than 25% urban land cover at these two scales did not vary significantly by hydrologic condition. 

Human viruses were analyzed for a subset of XX samples from the watershed and YY samples from subwatershed-scale sites concurrently with the human-associated and the general indicator bacteria, providing a means to assess potential exposure to human pathogens from sampled water. The fraction of samples for which human viruses were present increased with increasing sHM concentration, but occurrence of human viruses did not increase with increasing concentration of the non-specific fecal indicators E. coli and enterococci (Figure \@ref(fig:VirusOccurrenceFig)). These results reinforce the the assumption that human-associated bacteria markers represent presence of sewage and an increased risk of exposure to human pathogens with increasing human-associated bacteria concentrations.

```{r VirusOccurrenceFig, dpi=300, fig.width=3,fig.height=5, fig.cap = "Fraction of human virus occurrence as compared to concentration bins for A. the sum of human associated bacteria, B. Escherichia coli, and C. Enterococci in samples from subwatersheds of the Milwaukee River (subwatershed scale), and tributaries of the Great Lakes (watershed scale). Number of observations in each concentration bin are provided above the bars. sHM concentration of 450 Copy Number/100mL represents the analytical detection level. E. coli concentration of 235 CFU/100mL represents a common recreational water quality criteria.", echo=FALSE}

print(bacteria_vs_virus)

```

  + Bin sHM into the same categories as GLRI Phase I report
    + Graph virus %occurrence vs sHM bins
    + Is there a stats technique to do this? Categorical logistic regression?
       + test

## Regression Modeling
Regression models were explored for describing variability of human-associated bacteria using optical signals. The first consideration in regression modeling was the choice of sites to include in common models. Watershed and subwatershed sites were initially grouped together for a unified model. These efforts resulted in poor cross-validated predictive capability, and no adequate models were discovered. Next, categories from watershed and subwatershed sites were chosen for similarity in land cover and potential diversity of water quality influences as well as geographic proximity. These groups were chosen to minimize differences in background DOC that could lead to confounding signals in regressions, resulting in four site categories: Watershed-scale sites were separated into three categories for model development including Agricultural (Maumee, Portage, and Raisin), Urban (Clinton and Rouge), and single site (Milwaukee), and the three subwatershed-scale sites were included as the fourth category. Separating sites into these four categories resulted in improved cross-validated predictive capability for resulting models over the watershed- and subwatershed-scale unified model, so the four categories were selected for inclusion in final model development (Table \@ref(tab:tabTest)). 

Model development attempts for the small-scale sites also included four data groupings: first, data from all sites and samples within the three regions were used to develop one unified model, and second, separate data sets from each of the three regions was used to develop individual models. Resulting models for small-scale sites were all considered to be inadequate for the intended purpose: To meet sensor development needs for tracing contamination back to the source, regressions must provide increasing predictions with increasing human bacteria concentrations for individual events within a storm sewer system or small drainage basin. Attempts to develop models for the small-scale sites did not result in models that consistently met this need.

Table \@ref(tab:tabTest) using table 1 function.

```{r tabTest, echo= FALSE}
source("./Report/Tables/Table1.R")
table_1 <- make_table_1(model_summary)
table_1 <- set_caption(table_1, "Table: (\\#tab:tabTest)")
table_1
```

  + Mention seasonal interaction terms
  + Mention site terms in LMER routine
  + Sensors vs non-cor

Describe models selected

  + Two models were selected for each organism/site grouping combo
  + sensor variables = F, T, Turbidity + seasonality + mixed effect with sites
  + Same variables for all response variables
  + additional signals did not improve regressions over sensor signals
  + Two models were selected for each organism
 
Models were developed with two sets of optical variables: First, using optical signals to represent those used in commercially available field sensors (sensor models), and second, using additional optical signals that were not highly correlated with at least one of the sensor signals (alternate signal models). Two important attributes of the selected models included interaction of the optical variables with a seasonal term, and, for multi-site models, use of individual sites as random effects in the mixed effect models. The seasonal term was used to control for variable DOC presence as vegetation cover changed throughout the year and as soil contact of runoff varied with snow cover. Individual sites were used as random effects to help control for variable background DOC in watersheds resulting from different geologic environments and land cover. Model exploration with and without the seasonal and random effects terms verified that inclusion of these two model attributes resulted in improved model fit. 

The sensor models included different combinations of fluorescence signal "T" (often referred to as tryptophan-like fluorescence), fluorescence signal "F" (often referred to as "CDOM" or "fDOM"), and turbidity. T and F were commonly included in final models as interaction terms with seasonality. All final sensor models included turbidity, indicating that turbidity may be the most valuable signal for inclusion in these surrogate models with additional optical signals and seasonal terms to enhance accuracy of theses models. 

There was not a consistent substantial improvement in cross-validation error (root mean squared error, RMSE)  in the alternate signal models compared to the sensor models (Table \@ref(tab:tabTest)). The enterococci culture models for the urban large watershed sites and for the Milwaukee River site were the only two models that had 10% or greater decrease in RMSE by using models developed with the alternate signal variables. In addition to T and F, variables in the alternate signal models included two fluorescence signals (M and N), ratios of fluorescence signals, the fluorescence index, and ratios of absorbance signals (Table SI-XX). Collectively, results suggested that there may be minor improvements in model performance by use of the alternate signal variables for a few selected site-organism combinations, but that the optical signals selected for the alternate signal models are not consistent.

The proportion of virus occurrence increased with the sum of fitted sHB (Figure \@ref(fig:PredictionToVirusFig)). For instances when fitted model values were below 1000 copy number/100mL, no viruses were detected. Virus detection increased with increasing concentration up to 40% virus detection when sHB fitted values were greater than 100000 copy number/100mL. Because human viruses were measured independently from human bacteria and not used in model development, this result provides independent verification that the sensor models have the capability of predicting the presence of sewage and potential risk from human pathogens. 


```{r PredictionToVirusFig, dpi=300, fig.width=3,fig.height=2, fig.cap = "Fraction of human virus occurrence as compared to concentration bins for the sum of human associated bacteria computed from fitted values from regression models developed using laboratory-measured optical signals that represent currently available optical sensors. Number of observations in each concentration bin are provided above the bars. sHM concentration of 450 Copy Number/100mL represents the analytical detection level.", echo=FALSE}

print(Prediction_vs_virus)

```



EXAMPLE FOR FONT STYLE
<div custom-style="RedText">Whole paragraph of colored text</div>




# Discussion

**General sHM presence**

The variability of contamination level by watershed was illustrated by the wide variability in the level of contamination among watersheds included in this study with median concentrations of sHB varying from less than the detection limit in samples from watershed scale to greater than 10000 cn/100 ml in several samples from the small-scale sites within the Kinnickinic River watershed. The general increasing human virus occurrence with increasing concentration bins for sHB provided validation that human-associated bacteria markers can be valuable for assessing the presence of sewage and risk of exposure to sewage-contaminated waters. Exposure to waterborne viruses has been associated with a risk of human illness CAN WE INCLUDE AN EPI STUDY HERE? ADD SOME TEXT ON QMRA AND EPI STUDIES (exposure studies from beach citations, Corsi et al., 20xx--beaches, Chicago risk study, others?). Viruses, however, are not consistently present in the human waste stream, and when they are present, they are highly variable even in raw wastewater (Lenaker et al, 2018,  **<span custom-style="OrangeText">others with raw sewage data for viruses?</span>**). These pathogens are most likely to be present in wastewater when they are present in the human population, and concentrations are likely to vary depending on how pervasive they are in the human population at the time of sampling. Depending on the specific virus, the occurrence and magnitude of virus presence in wastewater can be seasonal (Lenaker et al, 2018, **<span custom-style="OrangeText">Other?</span>**). Conversely, presence of human-associated bacteria such as the two measured in samples from the current study are relatively stable in wastewater treatment plant influent over time with concentrations of approximately (**CHECK THIS NUMBER**) 10^7^ cn/100 ml $\pm$ an order of magnitude (Lenaker et al., 2019). With a detection level of 225 cn/100 ml, HIB would be detectable even after dilution in natural waters of four to six orders of magnitude. Therefore, while human-associated bacteria are likely to be present whenever human viruses are present, human viruses are not always present in environmental waters contaminated with human-associated bacteria. Depending on monitoring objectives, these two types of parameters can be valuable in different ways. Measurement of human viruses provide more direct information on human health risk while human-associated bacteria provide information on the potential for human health risk (McLellan et al., 20xx (QMRA for lachno), other QMRA for human bacteroides) and an additional level of information on wastewater prevalence that can include other contaminants that are potentially harmful to aquatic life regardless of pathogenic presence.

<div custom-style="RedText">Whole paragraph of colored text</div>

The lack of relation between EC or ENT and virus occurrence is consistent with conclusions from previous work that general fecal indicators are not necessarily good predictors of waterborne pathogens (**<span custom-style="OrangeText">add citations Corsi et al., beaches, +others</span>** ). These indicators are, however, used commonly as more general indicators of nonspecific fecal contamination from numerous sources (citations), and have previously been associated with a risk to human health (EPA epi studies). Concentrations of fecal indicator bacteria in recreational waters are a primary measure currently used for issuing swimming advisories for the protection of human health (**<span custom-style="OrangeText">add EPA recreational criteria reference here</span>**).


**<span custom-style="OrangeText">does this section belong in the methods as site description?</span>**
The result that model fit improved using selected subsets of the data by site rather than full data sets for each of the large watershed and subwatershed scales indicates an importance of watershed setting. Each subset of data represented a specific type of watershed setting with potential for distinctly different background DOC that could impact the relation between optical signals and bacteria abundance: The final subsets of data included large watersheds dominated by agricultural influence, large watersheds dominated by urban influence, a mixed land use watershed with seiche effect from Lake Michigan, and subwatersheds dominated by urban influence. The agricultural watersheds are located in the Western Lake Erie drainage basin and all have > xx% agricultural influence (**<span custom-style="OrangeText">add reference here</span>**). The urban watersheds were located in the Detroit metropolitan area, and both have active combined sewer overflows at times (**<span custom-style="OrangeText">add reference here</span>**). The Milwaukee River includes a mix of urban and agricultural land use and is influenced by a regular seiche effect that includes transitional influences from the Milwaukee River, the Milwaukee harbor, and Lake Michigan resulting in a unique combination of DOM sources. The subwatershed sites are all within the Menomonee River watershed in the Milwaukee metropolitan area that is dominated by residential, commercial, and industrial land cover, and to a lesser extent, the upper portion of the Menomonee River includes some agricultural influence. 

**Variable selection**
 
 IMPORTANT TO INCLUDE HERE: The gain in accuracy may not warrant development of multiple additional sensors for only a small gain in accuracy. 
 
 Inclusion of seasonal variables in the large watershed and subwatershed regressions suggest a 


**Seasonality**

  + inclusion of seasonal term suggests seasonality in the relation between bacteria and optical properties of water
  + seasonality in DOM/DOC/optical has been documented previously in streams, lakes, marine (maybe stick to streams?
  + Consider reasons for seasonality: vegetation changes, contact with soils and vegetation--less in winter, leaf leachate in the fall
  

Seasonality? 
    + Reference GLRI report?
    + Seasonality in streams: Phong et al, 2014; Yang et al., 2019
    + Seasonality in marine: Elisabeth Minor et al., 2006; Su et al., 2015
    
    


**Small scale variability**

Small scale sampling included storm sewers, ditches, and small streams in urban areas. These sites drained small areas, and therefore, have relatively small flows that can be greatly influenced by contamination from individual discharges (e.g misconnections or leaks from single sources). Depending on the nature of the individual contamination source and timing of the discharge in relation to sample collection times, DOC (and therefore optical signals) and human-associated bacteria can vary widely. Wastewater contamination from these individual sites can include sources such as laundry, bathing, and industrial waste that do not necessarily contain human waste, but will have influence on optical signals, and some sources contain human waste that will have great influence on human bacteria as well as optical signals. This type of variability is illustrated in sample results from local sanitary sewers during the sampling events for small scale sites: Concentrations of sHM in local sanitary sewers varied by three orders of magnitude and fluorescence signals T and F varied more than 2 orders of magnitude in these samples (figure SI-xx boxplots). The concentrations of DOC in local sanitary sewers varied from concentrations less than most environmental samples to concentrations greater than the regional WWTP collector samples (2.6-149 mg/L). This type of variability in the targeted contamination source presented a challenge for model development which requires a relatively consistent source signal.  

In addition, other non-human sources can influence the optical signals in an unpredictable manner such as, wildlife waste, pet waste, and leaf leachate. This is likely to be another substantial reason that modeling attempts were unsuccessful for small-scale sites. In contrast, flow contributing to the watershed and subwatershed sites represents water from many diverse, small-scale sources that are homogenized in the main channel, making it more likely to result in a consistent relationship between optical signals and human bacteria to facilitate model development. This difference among different scale sites is a likely reason that development of models for small scale sites was not possible while reasonable models were achievable for the watershed and subwatershed scale sites. 



**<div custom-style="BlueText">Info on FIB models and pathogen models in surface water (first milwaukee paper, beach paper, others?)</div>**

**Previous surrogate models for microbial contaminants**

Previous efforts have developed surrogate models for prediction of fecal indicators in recreational waters (Francy GL beaches, Whitman citation(s), Nevers citations, Brooks, PLS, Brooks, beauty contest, other), and in rivers (Dila et al. 2018, Corsi et al., Baldwin et al MMSD, Kansas pubs, +others). These models often use basic water quality parameters such as turbidity and water temperature as well as physical parameters such as wave height, water currents,  wind velocities, and stream flow as predictor variables. Some have been used in assisting managers of recreational waters for swimming advisories (citations), and others for helping to understand dynamics of water quality or for computation of stream loadings (**<span custom-style="OrangeText">Kansas pubs, Dila et al, 2018, Baldwin MMSD, others?</span>**). The majority of these modeling efforts have focused on prediction of general fecal indicators such as E. coli or fecal coliform (**<span custom-style="OrangeText">Enerococci??</span>**) that provide general microbial contamination, but do not necessarily indicate presence of wastewater and its associated pathogenic and chemical contamination. Inclusion of human-associated bacteria in the modeling effort provides opportunity to gain information on the level of wastewater contamination that is directly associated to breaches in the sanitary conveyance system that IDDE efforts could work to identify and control.

**Limitations of application**

  + Individual site calibration needed--no universal relationship
  + Sensor accuracy and reliability
    + translation of optical measurement to a field setting: how accurate? How stable over time?
    + turbidity and temperature effects
    + biofouling
    + general complications of operating sensors over long term: mechanical issues:
    + Representativeness
      + placement of sensors
      + in-stream vs flow-through: access issues for maintenance, complications of particle suspension, ...
      

#Conclusions

CONCEPTS TO INCLUDE: 

  + Three tiers of information: viruses/pathogens, HIB, optical. All have their place for evaluation of the influence of wastewater contamination.
  + Viruses: actual pathogens and verification of risk, validation of sewage presence
  + HIB: Continuous source in sewage: present if sewage is present, so in some cases, this may be a better marker to evaluate sources of sewage
  + Optical: Provide fine-time step and opportunity to compute more accurate loadings: allow managers to zero in on regions of watershed with the largest sources. more practical economical way to provide continuous data than discrete samples.
  +Limitations: 

 
#References


# Actions needed:
1. Develop site characteristics table. Land cover for the watershed and subwatershed scales, and for the three primary small watersheds in the small scale.
    + need site IDs for middle branch Clinton and Red Creek, NY
2. Investigate seasonality in bacteria data alone and in optical data alone.
  + add seasonality into the discussion
  
3. Add info on alternate signals and why it's probably is not worth it.

4. Retrieve and plot the local vs regional sewage data. Add that into the discussion.

5. Human-associated bacteria markers (CHECK NAME CONSISTENCY) 

6. Search for modeling of human-associated bacteria

7. 



Modeling points to make:

1. MMSD: 
  + a. There were three CSO events for subwatershed models. All three of these are outliers in the model. The model under-predicts these values for all bacteria modeled. Adding a CSO term aligns these with the rest of the model (adjustment of the intercept), but three observations is not enough to provide confidence in that model term. Additional CSO event samples would be needed to provide sufficient confidence in these results.


