--- 
title: "GLPF Manuscript"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
colorlinks: yes
lot: yes
lof: yes
fontsize: 12pt
monofont: "Source Code Pro"
monofontoptions: "Scale=0.7"
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
favicon: "favicons/favicon.ico"
description: "Getting ready for manuscript."
---

# Preface {-}

Placeholder



<!--chapter:end:index.Rmd-->


# EEM plot {#EEM}

Maybe we want to show a particular EEM plot...such as Figure \@ref(fig:eem-example).

```{r eem-example, fig.cap="Here is a EEM plot.", echo=FALSE}
print(EEMplot)

```

Pretty neat.

Here's the base-R figure (\@ref(fig:base-r)):

```{r base-r, fig.cap="Lachno vs HumBac"}
base_plot(summaryDF)

```

<!--chapter:end:01-EEM.Rmd-->

--- 
title: "GLPF Results Section"
date: "`r Sys.Date()`"
#site: bookdown::bookdown_site
#output: bookdown::gitbook
#documentclass: book
output: html_document
# colorlinks: yes
# lot: yes
# lof: yes
# fontsize: 12pt
# monofont: "Source Code Pro"
# monofontoptions: "Scale=0.7"
# bibliography: [book.bib, packages.bib]
# biblio-style: apalike
# link-citations: yes
# favicon: "favicons/favicon.ico"
# description: "Developing Results Section."
---

# Results {#results}

Results \@ref(fig:figure_2).

```{r figure_2, fig.cap="Figure 2. Human bacteria marker A. concentrations and b. Occurrence proportion in samples from small storm sewers and open channels (Small), subwatersheds of the Milwakee River (Subwatersheds), and tributaries of the Great Lakes (Watershed)", echo=FALSE}
print(fig_2)

```

Points to make with this figure:
1. Wisconsin small scale had samples with max concentrations and were generally higher than other sites
2. Many sites had greater concentrations during runoff events. This is true for the watersheds and subwatersheds that had substantial urban influence. 
3. Small scale sites


<!--chapter:end:Results.Rmd-->

